# Introduction {#intro}

## Terminology

The following terms come up repeatedly in discussion of machine learning[@GoogleRulesML]:

* **Instance**: The thing about which you want to make a prediction. For
example, the instance might be a web page that you want to classify as either
"about cats" or "not about cats".
* **Label**: An answer for a prediction task; either the answer produced by a
machine learning system, or the right answer supplied in training data. For
example, the label for a web page might be "about cats".
* **Feature**: A property of an instance used in a prediction task. For example,
a web page might have a feature "contains the word 'cat'".
* **Feature Column**: A set of related features, such as the set of all possible
countries in which users might live. An example may have one or more features
present in a feature column. "Feature column" is Google-specific terminology. A
feature column is referred to as a "namespace" in the VW system (at
Yahoo/Microsoft), or a field. Example: An instance (with its features) and a
label.
* **Model**: A statistical representation of a prediction task. You train a
model on examples then use the model to make predictions.
* **Metric**: A number that you care about. May or may not be directly
optimized.
* **Objective**: A metric that your algorithm is trying to optimize.
* **Pipeline**: The infrastructure surrounding a machine learning algorithm.
Includes gathering the data from the front end, putting it into training data
files, training one or more models, and exporting the models to production.

## Useful Materials

- [`bookdown`: Authoring Books and Technical Documents with R Markdown](https://bookdown.org/yihui/bookdown/)
- [`papaja`: Reproducible APA manuscripts with R Markdown](https://crsh.github.io/papaja_man/)

## Prerequisites


## Example

You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(intro). If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \@ref(methods).

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```